### 2017-11-15 Draft2/AsymptoticNotation.tex
Duplicate note

{\HdrNote} In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.

>>>>

{\HdrNote} In the following theorems, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.
